---
title: "Matrix"
output: html_document
---
## A matrix is actually a vector with an additional attribute (dim) which is itself a numeric vector with length 2, and defines the numbers of rows and columns of the matrix. A matrix can be created with the function matrix
```{r setup, include=FALSE}
matrix(data=5, nr=2, nc=2)
```

```{r}
matrix(1:6, 2, 3)
```
Another way to create a matrix is to give the appropriate values to the
dim attribute (which is initially NULL):

```{r}
x <- 1:15
x
dim(x)<- c(5, 3)
x
```
Data frame. We have seen that a data frame is created implicitly by the
function read.table; it is also possible to create a data frame with the
function data.frame. The vectors so included in the data frame must
be of the same length, or if one of the them is shorter, it is \recycled" a
whole number of times:

```{r}
x <- 1:4; n <- 10; M <- c(10, 35); y <- 2:4
data.frame(x, n)
```
```{r}
data.frame(x, M)

```

## Time-series. The function ts creates an object of class "ts" from a vector (single time-series) or a matrix (multivariate time-series), and some options which characterize the series. The options, with the default values,are:

## ts(data = NA, start = 1, end = numeric(0), frequency = 1,deltat = 1, ts.eps = getOption("ts.eps"), class, names)

## example:
```{r}
ts(1:10, start = 1959)
Start = 1959
End = 1968
Frequency = 1
ts(1:47, frequency = 12, start = c(1959, 2))
```

```{r}
ts(1:10, frequency = 4, start = c(1959, 2))
```
```{r}
ts(matrix(rpois(36, 5), 12, 3), start=c(1961, 1), frequency=12)
```

